An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-04 tex/paper.tex
Ideas for implications section

S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
hard_majo changes the results). ZD strategies do not fare well in many tournaments.

@@

>>>>

S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
hard_majo changes the results).

@@

Ideas for this section:
* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
even ZDGTFT2
* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
fare well
* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
foolmeonce, gruder
* It's possible to be generally cooperative and still exploit naive strategies effective,
such as LookerUp and MetaHunter
* Long memory strategies are generally better
* Meta strategies fare very well in general
* Variance of score distributions is surprisingly low

Plot of memory_depth vs mean score, mean wins?
